Automatically generated NE tagged corpora for English and Hungarian

### 2012-03-25 paper/engNERwiki.tex
Cut a few words...

There are several ways to improve the method described above to increase precision, sentence coverage and to account for peculiarities in the CoNLL guidelines. These are detailed in the next sub-sections.

>>>>

The following sub-sections describe how the method explained above can be improved to increase precision, sentence coverage and to account for peculiarities in the CoNLL guidelines.
